Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2025-01-20 Manuscript/src/sections/titleAbstract.tex
Updates from Overleaf

        We compared the accuracy of the two \ac{pmv} models, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that overall both models only predict \ac{tsv} correctly only one third of the times.
        The \ac{pmv-ce} has higher bias than \ac{pmv} in predicting thermal sensation in the subset of data with \acl{vr}~$\geq$~\qty{0.2}{\m\per\s}.
%        todo manually check values
        Both models have an accuracy lower or equal to \qty{5}{\percent} when predicting either `warm', `hot', or `cold'.
        This value is lower than random guessing (\qty{14}{\percent}), meaning they are misleading users.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Hence, we suggest reducing the applicability limit of both models within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        Finally, the assumption that individuals who feel `slightly warm' or `slightly cool' can be considered thermally neutral leads to under-counting thermal discomfort.
%        todo manually check values
        In the \acl{db2}, \qty{68}{\percent} of participants who were `slightly warm' wanted to be `cooler' and \qty{54}{\percent} of participants who were `slightly cool' wanted to be `warmer'.
    \end{abstract}

>>>>

        We compared the accuracy of the two \ac{pmv} models, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that overall both models only predict \ac{tsv} correctly only one-third of the time.
        The \ac{pmv-ce} has a higher bias than \ac{pmv} in predicting thermal sensation in the subset of data with \acl{vr}~$\geq$~\qty{0.2}{\m\per\s}.
%        todo manually check values
        Both models have an accuracy lower or equal to \qty{5}{\percent} when predicting either `warm', `hot', or `cold'.
        This value is lower than random guessing (\qty{14}{\percent}), meaning they are misleading users.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Hence, we suggest reducing the applicability limit of both models within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        Finally, the assumption that individuals who feel `slightly warm' or `slightly cool' can be considered thermally neutral leads to under-counting thermal discomfort.
%        todo manually check values
        In the \acl{db2}, \qty{68}{\percent} of participants who were `slightly warm' wanted to be `cooler' and \qty{54}{\percent} of participants who were `slightly cool' wanted to be `warmer'.
    \end{abstract}
